Joint Training of Classification and Similarity Models for \\ Intention Detection in Task-specific Chatbot

### 2020-09-10 chatbot_classification/aaai_2021/paper.tex
modified:   paper.tex

  \begin{abstract}
    Task-specific  chatbot systems have gained many important applications, such
    as  Siri,  Google home, and customer service systems, etc. One essential technique 
    underlying these applications  is to detect the real intention behind a user's input.
    The intention detection,  assuming  only  one  intention  in  a  user's input here, can be
    regarded  as  a  short  text  classification problem.  In  practice,  the  number  of
    intentions  can  be hundreds of thousands, as opposed to a few number in the
    traditional text classification problem; creating enough training data from tons of 
    raw user logs with miscellaneous information is not trivial, 
    and generally only 10 to 20 samples per intention are available in  the  early  stage.  
    Thus,  how  to  train  an  effective short-text classification model with limited training
    example in such a practical  and important application is critical. In this work, we propose a
    novel  model, called similarity model fused with classification model (SFC),
    which  combines  a  classification  model  and  a similarity model, and also
    borrows  the  power  of  multi-task  training  as well. We conduct extensive
    experiments  on  4  public  and 1 private datasets. Experimental results
    show that our new model outperforms very strong baselines (i.e., BERT, RoBERTa and
    ALBERT based pretrained models) by 2 percentages in average accuracy.

>>>>

  \begin{abstract}
    Task-specific  chatbot systems have gained many important applications, such
    as  Siri,  Google home, and customer service systems, etc. One essential technique 
    underlying these applications  is to detect the real intention behind a user's input.
    The intention detection,  assuming  only  one  intention  in  a  user's input here, can be
    regarded  as  a  short  text  classification problem.  In  practice,  the  number  of
    intentions  can  be hundreds of thousands, as opposed to a few number in the
    traditional text classification problem; creating enough training data from tons of 
    raw user logs with miscellaneous information is not trivial, 
    and generally only 10 to 20 samples per intention are available in  the  early  stage.  
    Thus,  how  to  train  an  effective short-text classification model with
    limited labeled data  in such a practical  and important application is critical. In this work, we propose a
    novel  model, called similarity model fused with classification model (SFC),
    which  combines  a  classification  model  and  a similarity model, and also
    borrows  the  power  of  multi-task  training  as well. We conduct extensive
    experiments  on  4  public  and 1 private datasets. Experimental results
    show that our new model outperforms very strong baselines (i.e., BERT, RoBERTa and
    ALBERT based pretrained models) by over 2 percentages in average F1 score.
